Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-06-09 paper/paper.tex
Text from James

>>>>

Due to the special structure of the maximum common subgraph problem, the following property holds
throughout the search process using the CP model: any two variables either have domains with no
values in common (with the possible exception of \bot), or have identical domains. The algorithm
McSplit exploits this property, while exploring essentially the same search tree as the CP model.
Rather than storing a domain for each vertex in V(G) -- which results in redundant storage in cases
where domains are identical -- equivalence classes of vertices in V(G) are stored, and a set of
candidate vertices in H is stored for each equivalence class. This enables fast propagation of the
constraints and smaller memory requirements. In addition, the data structure enables good branching
heuristics to be calculated cheaply.
